---
title: "Using fwapgr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using fwapgr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(ggplot2)
library(sf)
library(fwapgr)
```

## Let's make a map of Yakoun Lake in Haida Gwaii, BC

We'll start by looking at the available layers
```{r}
fwapgr::fwa_list_layers()
```

...and which columns are in the 'fwa_stream_networks_sp' layer
```{r}
fwapgr::fwa_list_columns('fwa_stream_networks_sp')
```


Let's get Yakoun river from the 'fwa_stream_networks_sp' layer. We will include the 'blue_line_key' column as it will come in handy later.
```{r}
yakoun <- fwapgr::fwa_feature("fwa_stream_networks_sp", 
                              filter = "gnis_name = 'Yakoun River'", 
                              columns = c("blue_line_key"))

yakoun
```

Often we don't know the valid `gnis_name` or column names to filter by. We can use these convenience functions instead.
```{r}
yakoun2 <- fwapgr::fwa_search_gnis_streams("yakoun") %>%
  fwapgr::fwa_gnis_streams()

```

OK now let's get the Yakoun River watershed. It requires a `blue_line_key`, which we will get from the 'blue_line_key' column of the stream layer. 
```{r}
blue_line_key <- unique(yakoun$blue_line_key)
wshed <- fwapgr::fwa_watershed(blue_line_key)
```

Let's get all lakes within the bounds of the Yakoun River watershed. We will use `sf` package to get the bounding box.
```{r}
bbox <- sf::st_bbox(wshed)
lakes <- fwapgr::fwa_feature("fwa_lakes_poly", bounds = bbox)
```

Let's get modelled fish habitat data within our bounds. Note, this is in a different schema (not the default 'whse_basemapping' schema). We'll reclassify the 'fish_habitat' column as 'fish habitat' or 'not fish habitat'. 
```{r}
habitat <- fwapgr::fwa_feature("modelled_habitat_potential", schema = 'fish_passage', columns = "fish_habitat", bounds = bbox)

habitat$habitat <- grepl('non fish habitat', habitat$fish_habitat, ignore.case = TRUE) %>%
  ifelse('not fish habitat', 'fish habitat') %>%
  factor(levels = c('not fish habitat', 'fish habitat'))
```

Finally, let's clip the habitat and lake layers to the watershed using `sf::st_intersection`
```{r}
habitat <- sf::st_intersection(habitat, wshed)
lakes <- sf::st_intersection(lakes, wshed)

```

Make a map!
```{r dpi=300, fig.width=7, fig.height=7}
ggplot2::ggplot(data = yakoun) +
  ggplot2::geom_sf(data = wshed, lwd = 0.15) +
  ggplot2::geom_sf(data = habitat, aes(color = habitat), lwd = 0.2) +
  ggplot2::geom_sf(lwd = 0.3) +
  ggplot2::geom_sf(data = lakes, fill = "steelblue", lwd = 0.1) +
  ggplot2::theme(legend.title = element_blank(),
                 legend.position = "bottom")
```

